---
title: "R Project 1 - Hello R"
author: "Juan C. Rodriguez"
date: "Due Fed 3rd"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The file has 1846 rows. The data frame has 3 variables: dataset, x-values, and y values.

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

For this example, instead of using dino_data you're going to change the dataset to star_data. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. If done right, a graph of a star should pop up.



```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Now to calculate the correlation coefficient. You're going to pipe (%>%) your data set and then summarize the correlation between x and y.
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
As you can see, the value is bigger in the star_data than the value in the dino_data. about -0.0630 (star_data) > about -0.0645 (dino_data)

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
