---
title: "R Project 1 - Hello R"
author: "Juan C. Rodriguez"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_width: 11
    fig_height: 9
    highlight: espresso
    theme: sandstone
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The file has 1846 rows. The data frame has 3 variables: dataset, x-values, and y values.

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

For this example, instead of using dino_data you're going to change the dataset to star_data. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. If done right, a graph of a star should pop up.



```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Now to calculate the correlation coefficient. You're going to pipe (%>%) your data set and then summarize the correlation between x and y.
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
As you can see, the value is bigger in the star_data than the value in the dino_data. about -0.0630 (star_data) > about -0.0645 (dino_data)

### Exercise 4

For this exercise, we're going to plot a circle dataset. You're going to assign datasaurus_dozen to circle_data. Then filter and set dataset == cirlcle. Now use ggplot to visualize the data. Type which data to use and define the aesthetic mapping using x = x and y = y. To end this code, you're going to type geom_point to define the geometric shapes.

Before setting plotting the dataset, label your section. For this section, you're going to set it up as r plot-circle.
```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
Now to measuer the correleation coefficent of the circle dataset. Pipe the dataset and summarize in r correlating x and y.
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
This results in the value being smaller than the r of dino. The correlation coeffiecient of this dataset is -0.0683 and the r of the dino dataset is -0.0645

### Exercise 5

For this exercise, we're going to plot all the datasets together. First, you're going to add R chucks and label as "plot-all". Then write down the code to plot.

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + #facet the dataset variable, in 3 cols
theme(legend.position = 'none')
```

You're going to create another chunk here again and label it as "cor-all". For this section, you're going to calculate the correlation coefficient of all the graphs.

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print()
```

